Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-04 thesis/paper.tex
Drafts of RQ1 discussion

%%Describe the change 
Version 2.0 of the API has been designed around an event driven system, as such, it's not surprising that the old event system had to be re-implemented. The new event system is used by all features of the new API, for example events are sent when movement is detected by the camera. This event system is combined with the use of callbacks to create a robust event driven API.

@@

%%Describe the change 
The final re-implementation updated the parameter setting features of the API. This particular module had very few changes to it's functionality except for bringing into line, once again, with the new standard.

@@

The interviewee did shed some light onto why this change occurred. We were informed that in order to continue using this feature in 2.0 and in newer versions of the camera hardware, it would have to be re-implemented from scratch. A cost analysis was performed on taking this action and it was deemed that the impact would be minimal resulting in it's removal from the API.

@@

\section{Discussion}
Intro with a generic motivation for the study e.g. ``the results and insight into the API development suggest the following things'':

@@

\subsection{RQ1}

1. 
Added functionality is a major factor
-Requests from partners
-Business motive related to more functionality = more sold cameras

Overwhelmingly, the primary driving factor behind API evolution appears to have been the desire for new API functionality. We found strong evidence to suggest that most, if not all of the additions, re-implementations and functional changes were undertaken to include functionality that the partners desired.

2. 
Maintainablity is important, but where that was changed; funcitoanlity changes were alos made
While are important and while it was mentioend during the interview that the groomative changes would hav ehappend in any case, there is not clear evidence for that allows us to make this concrete/bold claim. 
*Maintianabikltuy/groomative changes usually affect many places (i.e. standardization is very important) (relate it to ripple effects paper)

3. 
Controlling the way the users use the applicaitons is very important (error handling, example code, interfaces)

4. 
Relate back to other literature and say that deprecations are preferred before removing, but that removing is recommended in certain cases (i.e when they really dont want ppl to use the function)
*Dont do it without investigating the possible effects of removing something
*Dont remove too much at once

5. 
Changes to documentation/example code are not important enough to drive changes to API, but they make up a large part of the change (although it's strictly updative (change cuz something else was changed))

6. Hardware was not a driving factor (is this mentioned enough in the prev secitons?)
Hardware hasn't direclty cotnributed to driving the evolution

>>>>

%%Describe the change 
Version 2.0 of the API has been designed around an event driven system, as such, it is not surprising that the old event system had to be re-implemented. The new event system is used by all features of the new API, for example events are sent when movement is detected by the camera. This event system is combined with the use of callbacks to create a robust event driven API.

@@

%%Describe the change 
The final re-implementation updated the parameter setting features of the API. This particular module had very few changes to its functionality except for bringing into line, once again, with the new standard.

@@

The interviewee did shed some light onto why this change occurred. We were informed that in order to continue using this feature in 2.0 and in newer versions of the camera hardware, it would have to be re-implemented from scratch. A cost analysis was performed on taking this action and it was deemed that the impact would be minimal resulting in its removal from the API.

@@

\section{Discussion}
Our results have been valuable in exploring the motives behind API changes and the causes of API evolution. When Analysing these results, the following interesting topics came to light:

Intro with a generic motivation for the study e.g. ``the results and insight into the API development suggest the following things'':

@@

\subsection{How do companies actively drive API evolution?}

\noindent
\textbf{Adding functionality is a prime driver of API evolution  }
Overwhelmingly, the primary driving factor behind API evolution was the desire for new API functionality. We found strong evidence to suggest that most, if not all of the additions, re-implementations and functional changes were undertaken to include additional functionality requested both internally and by the API users. This focus upon functionality was also emphasised in part due to a business goal. The more features the API can provide, the more applications developers can create for the cameras. This has a knock-on effect of increasing the appeal and therefore value of the products.

%API users should be included in the design process?
\smallskip \noindent
\textbf{Maintainability does not drive change  } 
While maintainability is important, it is not a primary driving factor for change. We found that where maintainability changed, functionality was also altered. For example, we predicted that the main intents to be enhancive which was correct. Furthermore, of the changes identified, none were considered to be primarily groomative, groomative changes were only identified as sub-category changes. Changes to the example code is further evidence of this. The example code was updated purely to reflect the changes in functionality and not as a groomative effort.

\smallskip \noindent
\textbf{Aiding development of applications  } 
Aiding users of the API to create correct and robust applications is a very important evolution factor for Axis. Changes between the versions brought about improvements to error handling, the example code and the way in which the API utilises interfaces. This, coupled with removal of unwanted functionality and unsafe operations, has allowed the API to grow and become much more user friendly. As mentioned previously, this could increase the amount of applications being created for the camera and thus could increase its value.

\smallskip \noindent
\textbf{Removing functionality  }
Previous literature has stated that deprecations should be favoured over removals from API for many reasons except in specific circumstances. The successful removal of the burst function seems to indicate that this advice is well worth following. Indeed, axis only removed this function from the API after an internal review found that the cost of removing it would outweigh potential drawbacks to keeping it in the API. It is therefore recommended to only remove something if the effects of removing it have been well investigated and that the removal is rather small in scale.

\smallskip \noindent
\textbf{Updative changes do not drive change  }
Changes to documentation and example code are important, especially if the API is drastically changing between versions. However, these updative changes are drivers themselves, rather, they make up part of a larger change as a whole. 
%^Probably needs more to it?

\smallskip \noindent
\textbf{Hardware was not a driving factor  }
Interestingly, we found that hardware was not a direct driver of change. Initially we had thought that it would be one of the strongest drivers of change, for example, new versions of hardware become available or new hardware is added to the camera requiring something in the API to access it. This does seem to suggest that the hardware for the camera is sufficiently stable such that it does not require changes and that those changes do not need to be reflected in new API versions.
